---
title: "Common Functions"
output: html_notebook
---

Here are some of the common functions which are used in the simulation code.

```{r}
library(rstream)
## initialize streams of random numbers
gendemand <- new("rstream.mrg32k3a")
```
The library used for the codes is Rstream, which enables us to use CRN.
gendemand is a varable to store the stream of random numbers generated by the rstream library


```{r}
## Exponential RV
randexpo <- function (lambda,rs) {
  #U <- runif(1,0,1)
  U <- rstream.sample(rs,1)
  X <- -lambda*log(1-U)
  
  return(round(X))
}
```
This function is an exponential random variable generator. We use this to generate the interarrival times of the customers.
It takes in 2 arguments, the rate (lambda) and the stream of random numbers (rs), and returns a sample from the exponential distribution



```{r}
## Generates a random variable based on the mean and variance
#takes in mean, var and minimum values with default being std norm and no minimum
randnorm <- function (mean = 0,var = 1, min = -Inf) {
  sd = sqrt(var)
  out = max(min,rnorm(1,mean,sd))
  out = min(out,180)
  out
}
```
This functions is what we use to generate the service times for the food processing. 
It takes in 3 arguments, the mean, varience and a minimum value, and returns a sample from the normal distribution 
We set a minimum value for the service time (as taken from the minimum value of the service time observed)