---
title: "Initialization Size"
output: html_notebook
---

This function is used to simulate the traditional queue with different inital queue sizes. We use CRN to help reduce variance in comparison.
It uses the function to simulate traditional queue and the other RV generating functions.
It takes in 2 arguments, queue size (to test until) and number of iterations to run.
It returns the average wait times for each initial queue length, from 0 until the number specified.


```{r}
#Here we do a comparison for the average waiting times for different initial queue lengths

#input max queue length and number of iterations to run
dosim <- function(queue,iter=1){
  #run code
  AvgWaitTimes <- rep(NA,queue+1) #vector to store average wait times for each queue length
  
  #Run 1 iteration
  #Get the average wait times using intial queue length of 0-queue
  rstream.nextsubstream(gendemand);
  for (i in 0:queue){
    temp <- simulateOneRun_T(i,runtime, arrival1)
    AvgWaitTimes[i+1] <- temp[3]
    rstream.resetsubstream(gendemand);
  }
  
  iter = iter - 1
  #Repeat iter-1 times
  rep = 1
  while(iter>0){
    rstream.nextsubstream(gendemand);
    for (i in 0:queue){ 
      temp <- simulateOneRun_T(i,runtime, arrival1)             #Run simulation, get average time
      temp <- temp[3]
      old_mean <- AvgWaitTimes[i+1]                             #Store old avg in temp var
      new_mean <- old_mean + (1/(rep+1)) * (temp - old_mean)    #Calc new avg
      AvgWaitTimes[i+1] <- new_mean                             #Store new avg
      
      rstream.resetsubstream(gendemand);
    }
    rep = rep + 1
    iter = iter - 1  
  }
  
  return(AvgWaitTimes)
}
```

We run the function with a queue length of 10 as that is the mode of our observations.
We obtain an average wait time over 1000 iterations

```{r}
results = dosim(10,1000)
results
```


Then we plot a graph of Average Time against Queue length (the graph can be seen later on in Experimental Runs)
```{r}
library(ggplot2)
df <- data.frame(x=c(0:10),y=round(results))
ggplot(data=df, aes(x=df$x,y=df$y)) +
  scale_x_continuous(breaks = seq(0, 10, by = 1))+
  geom_point()+
  geom_line()+
  geom_text(aes(label=df$y),size=4, position = position_nudge(y = 10))+
  labs(x="\nInitial Queue Lengths", y="\nAverage Waiting Times (s)\n")+ 
  theme_classic()
```